\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% Starting
\name{Gaurav Raj Sharma}
\address{\faPhone \ \href{tel:9779860667795}{(+977)9860667795} \ \faEnvelope \ \href{mailto:gauravrajsharma053@gmail.com}{gauravrajsharma053}}
\address{ \href{https://github.com/GauravRajSharma} {\faGithub \ GauravRajSharma}}
\address{Kathmandu, Nepal}


\begin{document}

\begin{rSection}{Profile Summary}
    Full-Stack Software Engineer with {\bf 5+ Years} of experience designing and developing web applications. Proven ability to work across the entire development lifecycle, from frontend design to backend development and infrastructure deployment. Skilled in a variety of programming languages, frameworks, and tools, with experience leading engineering teams on various projects
\end{rSection}

\begin{rSection}{Qualification - Areas of expertise}
    \begin{itemize}
        \item {\bf Full-Stack Development: }Proven ability to design, develop, and deploy web applications from user interface (front-end) to data processing and storage (back-end) utilizing a diverse range of programming languages, frameworks, and tools.
        \item {\bf Infrastructure Management: }Expertise in setting up, managing, and scaling efficient deployment environments using tools like Docker, Kubernetes, and Linux, ensuring smooth application operation.
        \item {\bf Cloud Technologies: }Experience in leveraging cloud platforms like DigitalOcean and Azure to achieve scalable and reliable deployments, optimizing application performance and availability.
    \end{itemize}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Languages    & Python, Golang, JavaScript (Node.js and Browser), SQL         \\
        Technologies & TypeScript, Next.js, React, React Native, Vue.js, Django      \\
        Tools        & Git, Docker, Kubernetes, Linux, Bash, Nginx/Caddy, PostgreSQL \\
    \end{tabular}
\end{rSection}

\begin{rSection}{Education}
    {\bf Bachelor’s Degree in Computer Engineering\\Kathmandu Engineering College,
        Tribhuvan University\\Kathmandu, Nepal} \hfill 2019
\end{rSection}

\begin{rSection}{Relevant Experience [\textit{5 Years}]}
    % Ultra Tendency 
    \large{{\bf Ultra Tendency International GmbH}}
    \\ \small{\textit{\textbf{Full Stack Software Engineer}}} (\small{\textit{2022-present}})

    \begin{itemize}
        \item Built a multilingual web application with dynamic content editing and restructuring, improving user experience.
        \item Managed Azure deployment for the application, ensuring scalability and uptime.
        \item Troubleshooted production issues using Cosmos DB, GitHub Actions, and Azure pipelines, achieving system stability.
        \item Architected the system for efficient content management, simplifying multi-language updates.
        \item Developed a training module for the application, enabling course sales and distribution.
        \item Integrated payment processing within the training module for a seamless user experience.
    \end{itemize}

    \pagebreak
    % Connect US 
    \large{{\bf Kathmandu Metropolitan IT Department and Connect US Pvt. Ltd}}
    \\ \small{\textit{\textbf{Full Stack Software Engineer}}} (\small{\textit{2024 (Freelance)}})

    \begin{itemize}
        \item Developed a comprehensive IT project monitoring web application to streamline issue tracking and resolution.
        \item Unified project management for vendors and administrators, enabling features like task assignment, log updates, and status checks.
        \item Implemented automated SMS notifications for deadlines and improved communication.
        \item Enhanced vendor efficiency by allowing for log updates and document sharing, while providing the IT department with real-time project and deadline visibility.
        \item Enabled performance analysis for administrators through vendor-specific project reports.

    \end{itemize}

    % Bytefaucet
    \large{{\bf Bytefaucet Pvt. Ltd}}
    \\ \small{\textit{\textbf{Full Stack Software Engineer + Product Lead}}} (\small{\textit{2022-2024 (Freelance)}})

    \begin{enumerate}
        \item \textbf{Weather Visualization Software for Department of Meterology and Hydrology}
              \begin{itemize}
                  \item Led a team of engineers in developing visualization software for the Department of Hydrology, facilitating real-time weather data analysis.
                  \item Built a fault-tolerant automatic synchronization system to establish a national real-time weather database.
                  \item Developed visualizations for weather parameters across stations and interpolated grids for Nepal.
                  \item Created visualizations for various derived meteorological metrics.
                  \item Designed a high-performance data extraction system enabling efficient access to large datasets.
                  \item Optimized database performance with PostgreSQL and PostGIS for faster data processing.
                  \item Engineered a maintainable and extensible web application for report generation and data visualization.
                  \item Implemented automated data quality control to identify and flag invalid weather readings.
                  \item Established a low-maintenance system for continuous operation and minimal human intervention.
                  \item Enabled efficient visualization of large weather datasets from 1981 to present.
              \end{itemize}
        \item \textbf{Contract Information Management System}
              \begin{itemize}
                  \item Streamlined vendor contract management by facilitating recording and timely status updates.
                  \item Implemented comprehensive tracking for key contract aspects like PGBs, APGs, insurance, and work schedules.
                  \item Automated vendor communication with SMS notifications for document submission deadlines.
                  \item Built a robust reporting system for detailed contract insights and various scenarios.
                  \item Enabled efficient letter generation with dynamic template printing functionalities.
              \end{itemize}
    \end{enumerate}

    % Coresoft Integrated Nepal
    \large{{\bf Coresoft Integrated Nepal Pvt. Ltd.}}
    \\ \small{\textit{\textbf{System Architect + DevOps Engineer}}} (\small{\textit{2021-2022 (Freelance)}})

    \begin{itemize}
        \item Established scalable and reliable infrastructure for multiple projects on DigitalOcean using Kubernetes.
        \item Implemented CI/CD pipelines across development, staging, and production environments for streamlined deployments.
        \item Provided comprehensive infrastructure support to development teams, resolving issues and ensuring smooth operation.
        \item Contributed to software architecture, database design, and workflow creation for various product teams.
        \item Offered technical expertise in React, React Native, Node.js, Kubernetes, Docker, DigitalOcean, and PostgreSQL to support development teams.
    \end{itemize}

    % National Disaster Risk Reduction And Management Authority
    \large{{\bf National Disaster Risk Reduction And Management Authority}}
    \\ \small{\textit{\textbf{Frontend Engineer}}} (\small{\textit{2021-2022 (Freelance)}})

    \begin{itemize}
        \item Built a web application for the Nepal government to streamline disaster data collection, storage, and management.
        \item Implemented automated data features for efficient and accurate data entry, updates, and secure storage.
        \item Integrated payment rollout management for coordinated tracking of disaster relief funds.
    \end{itemize}


    % Fiberknot Digital Pvt. Ltd.
    \large{{\bf Fiberknot Digital Pvt. Ltd}}
    \\ \small{\textit{\textbf{Full Stack Software Engineer}}} (\small{\textit{2020-2022 (Full Time)}})

    \begin{enumerate}
        \item \textbf{Complete Ecommerce Solutions}
              \begin{itemize}
                  \item Developed custom e-commerce solutions using modern web technologies for retail shops and local farms.
                  \item Implemented role-based access control for secure and tailored user experiences.
                  \item Empowered clients with rich text editors for easy content management and user engagement.
                  \item Built user-friendly CMS systems for efficient product management and business growth.
              \end{itemize}

        \item \textbf{Automated Accounting and Tax Filling System for Ecommerce Vendors}
              \begin{itemize}
                  \item Built a full-fledged web application for seamless connection and management across diverse digital marketplaces and vendors.
                  \item Automated tax reporting by aggregating sales data from various platforms for efficient financial management.
                  \item Implemented real-time inventory tracking across multiple marketplaces, ensuring accurate stock visibility.
                  \item Developed a streamlined vendor communication system for efficient collaboration across marketplaces.
                  \item Simplified order tracking and receipt generation for customers, enhancing user experience across all sales channels.
              \end{itemize}
    \end{enumerate}

    % Podamibe Pvt. Ltd
    \large{{\bf Podamibe Pvt. Ltd}}
    \\ \small{\textit{\textbf{Full Stack Junior Software Engineer}}} (\small{\textit{2019-2020 (Full Time)}})

    \begin{enumerate}
        \item \textbf{Interactive Voice Response System.}
              \begin{itemize}
                  \item Developed a highly configurable IVR system adaptable to meet evolving business needs.
                  \item Integrated subscription functionalities within the IVR to boost user engagement and service offerings.
                  \item Built a user-friendly admin panel for efficient subscription tracking, recording updates, and IVR configuration.
                  \item Enabled data-driven decision making through comprehensive IVR analytics and subscription tracking.
              \end{itemize}

        \item \textbf{Subscription based auto-renewal Payment System}
              \begin{itemize}
                  \item   Developed a custom auto-renewal payment system for Merolagani, streamlining subscription management and renewals for their customers.
                  \item  Built a comprehensive dashboard for tracking key subscription metrics (total subscriptions, revenue) to support data-driven decisions and performance analysis.
              \end{itemize}

        \item \textbf{General Purpose e-Payment Integration System.}
              \begin{itemize}
                  \item Built an internal payment integration tool for seamless vendor connections in Nepal via a unified API, simplifying application development.
                  \item Empowered users with a user-friendly dashboard for transaction visibility, report generation, and access control, boosting operational efficiency.
                  \item Enabled real-time transaction monitoring and system analytics through a dedicated dashboard, driving performance optimization and informed decision-making.
              \end{itemize}

        \item \textbf{Platform agnostic log aggregation system.}
              \begin{itemize}
                  \item Built a queue-based automatic log aggregation system for efficient log processing and storage from diverse applications to various destinations. This ensures comprehensive record-keeping and simplifies report generation.
              \end{itemize}
    \end{enumerate}
\end{rSection}


\end{document}
